junk_final_assignment

### 2022-11-27 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

df$party <- ifelse(str_detect(df$Sponsor, "R-[A-Z]{2,}"),"Republican", ifelse(str_detect(df$Sponsor,"D-[A-Z]{2,}"),"Democrat", NA))
```

@@

#Wordcloud comparing Democrats and Republicans
```{r}
dfmat2 <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$party) %>%
    dfm_trim(min_termfreq = 3)

>>>>

df$Party <- ifelse(str_detect(df$Sponsor, "R-[A-Z]{2,}"),"Republican", ifelse(str_detect(df$Sponsor,"D-[A-Z]{2,}"),"Democrat", NA))
```

@@

#Wordcloud comparing Democrats and Republicans
```{r}
dfmat2 <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$Party) %>%
    dfm_trim(min_termfreq = 3)
